Final Report

### 2022-05-06 Final Report.Rmd
tables with labels

@@

>>>>

joined_select <- full_join(joined_high, joined_low)

@@

> Let's see how this is different from continent to continent

```{r}
#Mean total deaths for each continent
deaths_north <- na.omit(north_america)  %>% 
  group_by(country) %>% 
  summarize(north_america_deaths = mean(total_deaths))

deaths_south <- na.omit(south_america)  %>% 
  group_by(country) %>% 
  summarize(south_america_deaths = mean(total_deaths))

deaths_africa <- na.omit(africa)  %>% 
  group_by(country) %>% 
  summarize(africa_deaths = mean(total_deaths))

deaths_europe <- na.omit(europe)  %>% 
  group_by(country) %>% 
  summarize(europe_deaths = mean(total_deaths))

deaths_asia <- na.omit(asia)  %>% 
  group_by(country) %>% 
  summarize(asia_deaths = mean(total_deaths))

deaths_oceania <- na.omit(oceania)  %>% 
  group_by(country) %>% 
  summarize(oceania_deaths = mean(total_deaths))

#Table to view continent deaths 
kable(deaths_north, caption = "North America Average Death Count")
kable(deaths_south, caption = "South America Average Death Count")
kable(deaths_africa, caption = "Africa Average Death Count")
kable(deaths_asia, caption = "Asia Average Death Count")
kable(deaths_europe, caption = "Europe Average Death Count")
kable(deaths_oceania, caption = "Oceania Average Death Count")
